\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the PoC demo and the Rev
0 demo; the contributions prior to the PoC are NOT included.

\section{Demo Plans}

\subsection*{Overview}
The Rev 0 demo will be performed in-person and run locally from a group member's laptop. The goal is to demonstrate a complete two-player game flow with authentication, lobby management, and real-time gameplay via WebSocket communication.

\subsection*{Setup}
\begin{itemize}
    \item Start the backend server (\texttt{Node.js} with Express and Socket.IO) on the presenter's machine.
    \item Start the frontend development server (\texttt{Vite + React}) on the presenter's machine.
    \item Open the game in two separate browser windows (one normal, one incognito) to simulate two players.
\end{itemize}

\subsection*{Demo Flow (approx. 8--10 minutes)}
\begin{enumerate}
    \item Brief introduction of demo objectives and improvements since POC (30s).
    \item Demonstrate user authentication:
        \begin{itemize}
            \item Register/login for Player 1 in the normal browser window.
            \item Register/login for Player 2 in the incognito window.
        \end{itemize}
    \item Demonstrate lobby system:
        \begin{itemize}
            \item Player 1 creates a lobby and copies the lobby ID.
            \item Player 2 joins the lobby using the shared lobby ID.
            \item Player 1 selects numeral system (Dozenal/Decimal) and starts the match.
        \end{itemize}
    \item Show automatic transition from Lobby screen to Game screen for both players.
    \item Demonstrate real-time gameplay with the new UI:
        \begin{itemize}
            \item Show opponent's face-down hand and card count.
            \item Playing cards from visible hand with playability highlighting.
            \item Demonstrate wildcard (10) with suit picker modal and golden card styling.
            \item Demonstrate skip card (6) granting free play with blue card styling.
            \item Drawing cards when no valid plays are available.
            \item Show real-time score updates and turn indicators.
        \end{itemize}
    \item Demonstrate the Decimal/Dozenal display toggle in the game header.
    \item Drive the game toward an endgame state and show round/game completion.
    \item Conclude with current limitations and planned improvements for Rev 1, then take questions.
\end{enumerate}

\subsection*{Notes}
\begin{itemize}
    \item Authentication is now functional with JWT tokens stored in localStorage.
    \item WebSocket handles real-time game state synchronization between players.
    \item Will mention current limitations (local deployment only, basic error handling) and planned next steps (deployment, improved UI/UX, additional game modes).
\end{itemize}

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2 \\
Ruida Chen & 2 \\
Jiaming Li & 2 \\
Alvin Qian & 2 \\
Ammar Sharbat & 2 \\
\bottomrule
\end{tabular}
\end{table}

Explanation: \\\\
We don't meet that often as a team, rather we use Discord for communication generally, which is very hard to trace.\\\\
All team meetings we have had to date have been added our Github Repo. Here is our meeting \href{https://github.com/The-Crazy-Four-Games/Crazy-Tens-Game/issues/213}{last November}, and \href{https://github.com/The-Crazy-Four-Games/Crazy-Tens-Game/issues/163}{this January}.\\

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\noindent \textbf{Supervisor's Name: } [fill in this information]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & Num\\
Name 1 & Num\\
Name 2 & Num\\
Name 3 & Num\\
Name 4 & Num\\
Name 5 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture + Tutorial Attendance\\    OR  \\Lectures + Tutorials Read}

Except for teammate Ammar, all 3 members did not attent the majority of lectures, but they did read several of them as they were needed for project work.
As long as you read the lecture, your attendance will be counted in the total.

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1 \\
Ruida Chen & 1 \\
Jiaming Li & 0 \\
Alvin Qian & 0 \\
Ammar Sharbat & 1 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Tutorials}\\
\midrule
Total & 1 \\
Ruida Chen & 0 \\
Jiaming Li & 0 \\
Alvin Qian & 0 \\
Ammar Sharbat & 0 \\
\bottomrule
\end{tabular}
\end{table}

Explanation:\\\\
Note: Both tallies are not entirely accurate, because outside of Teammate Ammar and Teammate Ruida (for some), teammates have not checkmarked their attendance/reading of classes, so the number listed is are just based on teammate Ammar's best estimates of the project group's "attendance".\\
An issue exists in our \href{https://github.com/The-Crazy-Four-Games/Crazy-Tens-Game/issues?q=lecture\%20-}{GitHub Repository} for every lecture and tutorial class for the course.\\
This Team Contribution Report is only concerned our attendance of the \href{https://github.com/The-Crazy-Four-Games/Crazy-Tens-Game/issues/169}{lecture} and \href{https://github.com/The-Crazy-Four-Games/Crazy-Tens-Game/issues/231}{tutorial} this January, as these were the only classes since the POC Demo last November.

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Chris Schankula]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Ruida Chen & 0 \\
Jiaming Li & 0 \\
Alvin Qian & 0 \\
Ammar Sharbat & 0 \\
\bottomrule
\end{tabular}
\end{table}

Explanation:\\\\
Our project team (Team 25) had a TA switch after the first document discussion (PS+Goals \& DevPlan), from TA Rashad Bhuiyan to TA Chris Schankula.\\
TA Chris has been very helpful for our Team, though he was not available to meet for the most recent Document Discussion on DesDoc\_Rev0 despite Teammate Ammar reaching out on the week of January 12--16 2026.\\
Otherwise, our team has attended all other TA document discussions, and TA Chris has been very helpful and provided great feedback on our deliverables.

\section{Commits}

Time Period : January - now

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 21 & 100\% \\
Ruida Chen & 11 & 52.4\% \\
Jiaming Li & 2 & 9.5\% \\
Alvin Qian & 4 & 19.0\% \\
Ammar Sharbata & 4 & 19.0\% \\
\bottomrule
\end{tabular}
\end{table}

Different teammates use different commit styles—some prefer batching changes into a few large commits after completing a section, while others commit incrementally. As a result, the number of commits does not necessarily correspond directly to workload or contribution size.

\section{Issue Tracker}

Time Period : January - now



\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Ruida Chen & 13 & 12 \\
Jiaming Li & 9 &  14\\
Alvin Qian & 16 &  17\\
Ammar Sharbata & 13 & 2  \\
\bottomrule
\end{tabular}
\end{table}

Some issues were created long ago (e.g., from earlier lectures/meetings) but were only closed recently because they were left open unintentionally. These late-closed legacy issues do not reflect current work for this reporting period and are therefore excluded from the issue count.


\section{CICD}

\wss{Say how CICD is used in your project}

\section{Team Charter Trigger Items}

\wss{Provide a summary of the quantified triggers identified in the team's
charter.}

\wss{Provide a list of any violations of the triggers.  If the team wishes, the
violations can be summarized on aggregate, instead of naming specific team
members.}

\wss{Provide a plan to address the violations.  This could include revising the
triggers, if they are found to be too weak, strong or ambiguous.}

\section{Additional Productivity Metrics}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}